### 2018-02-13 paper/algorithm.tex

We have several participants: Alice, Bob, Carol and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to keep local knowledge in the 
swarm and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledge to coordinate file sharing between devices in different swarms.

@@

A user's devices, \(D_i\), uses the Device Swarm Protocol to coordinate 
themselves.
More specifically, the devices use this protocol to keep the swarm state up to 
date.
The swarm state contains:
\begin{itemize}
  \item A knowledge vector, \(A_i\), encoding a Markov chain to predict online 
    and offline patterns for the various devices to predict when and for how 
    long each device might be available before disappearing again.
  \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
    (\(N_i\)) to its devices (\(D_i\)) that store a copy of that file.
\end{itemize}

@@

All swarms participates in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(R\), of devices available for routing.
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}

>>>>

We have several participants: Alice, Bob, Carol and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

A user's devices, \(D_i\), use the Device Swarm Protocol to coordinate 
themselves.
More specifically, the devices use this protocol to keep the swarm state up to 
date.
The swarm state contains:
\begin{itemize}
  \item A knowledge vector, \(A_i\), encoding a Markov chain to predict online 
    and offline patterns for the various devices to predict when and for how 
    long each device might be available before disappearing again;
  \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
    (\(N_i\)) to its devices (\(D_i\)) that store a copy of that file.
\end{itemize}

@@

All swarms participate in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(R\), of devices available for routing;
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}
